### 2022-03-09 unif/unif.tex
MORE

As mentioned in Chapter \ref{ch:intro}, many of the reasoning systems deployed
in various areas of computer science and matemathics are based on variants of
higher-order logic. More often than not, they also require unification of
higher-order terms. Due to its undecidability and explosiveness, the
higher-order unification problem is considered one of the main obstacles on the
road to efficient higher-order tools.

>>>>

As mentioned in Chapter \ref{ch:intro}, many of the reasoning systems deployed
in various areas of computer science and mathematics are based on variants of
higher-order logic. More often than not, they also require unification of
higher-order terms. Due to its undecidability and explosiveness, the
higher-order unification problem is considered one of the main obstacles on the
road to efficient higher-order tools.
